### 2018-08-13 response/response.tex

Thanks to all the reviewers for their comments.

\section{Response to Reviewer 1}

\begin{verbatim}
Although the explanation of the problem and the solution is very
clear in general, I think that it would be useful to include an
explanation of how the mapping from virtual to physical addresses
could create additional conflicts in the shared cache, and an analysis
of whether this could happen in the target system or not.
\end{verbatim}

Added. See the new sentences added in lines -2 -- -1 in
page 10 and lines 1 -- 3 in Page 11 (Section 4).

@@

\begin{verbatim}
There is a typo on Page 7, line 43, turning -> tuning.
\end{verbatim}

Fixed.

\begin{verbatim}
As the authors mentioned the related work on the tuning implementation
of GEMM only, they should also review the work regarding cache 
partitioning because this paper discussion is mainly on cache
partitioning. Some important papers are: ...
\end{verbatim}

The recommended references are now cited and
discussed in the last paragraph of Section 5.

### 2018-08-13 evaluation.tex
Remove colored highlights

We have implemented SCP in the OpenBLAS~\cite{openblas} library
%% (version 0.3.0-dev)
and evaluated it on a Phytium 2000+ processor.
The Phytium 2000+ processor is an emerging high-performance
64-core processor based on ARM's AArch64 architecture.
The 64 cores are organized into 16 clusters with each
cluster containing four cores.
The structure of a cluster is almost the same as
the four-core processor in Figure~\ref{fig:hierarchy}
except that the L2 caches of all 16 clusters connect to the main memory
with hardware coherence.
Table~\ref{tab:cluster} lists the
architectural parameters for the cores and caches
in this processor
and Table~\ref{tab:software} shows the software environment used.
\textcolor{blue}{
The L2 caches in the Phytium 2000+ processor are physically indexed.
In our implementation, physically continuous
memory buffers (allocated by the \texttt{HUGETLBFS} filesystem
provided by the Linux kernel) are used for storing
matrices in packed form. Therefore,
for a given shared L2 cache,
the matrix data accessed by different threads 
are guaranteed to be free of conflict cache misses.
}
We restrict our evaluation to DGEMM,
as in prior work~\cite{blispar,augem,poetmicro}, for two reasons.
First, the basic idea behind SCP applies to other
variants of GEMM such as SGEMM, CGEMM and ZGEMM.
Second, the LINPACK benchmark, which is used to build the
TOP500 list of world's most powerful supercomputers~\cite{top500},
relies on the DGEMM variant.

@@

\textcolor{blue}{
The mairix sizes selected range from 3072 to 
4096 when $NT \in \{4, 8\}$ and to 
6144 when $NT \in \{16, 32, 64\}$. 
These sizes are large enough to make GEMM run stably at peak performance
the given the total number of threads participating in the computation.
}

>>>>

We have implemented SCP in the OpenBLAS~\cite{openblas} library
%% (version 0.3.0-dev)
and evaluated it on a Phytium 2000+ processor.
The Phytium 2000+ processor is an emerging high-performance
64-core processor based on ARM's AArch64 architecture.
The 64 cores are organized into 16 clusters with each
cluster containing four cores.
The structure of a cluster is almost the same as
the four-core processor in Figure~\ref{fig:hierarchy}
except that the L2 caches of all 16 clusters connect to the main memory
with hardware coherence.
Table~\ref{tab:cluster} lists the
architectural parameters for the cores and caches
in this processor
and Table~\ref{tab:software} shows the software environment used.
The L2 caches in the Phytium 2000+ processor are physically indexed.
In our implementation, physically continuous
memory buffers (allocated by the \texttt{HUGETLBFS} filesystem
provided by the Linux kernel) are used for storing
matrices in packed form. Therefore,
for a given shared L2 cache,
the matrix data accessed by different threads 
are guaranteed to be free of conflict cache misses.
We restrict our evaluation to DGEMM,
as in prior work~\cite{blispar,augem,poetmicro}, for two reasons.
First, the basic idea behind SCP applies to other
variants of GEMM such as SGEMM, CGEMM and ZGEMM.
Second, the LINPACK benchmark, which is used to build the
TOP500 list of world's most powerful supercomputers~\cite{top500},
relies on the DGEMM variant.

@@

The mairix sizes selected range from 3072 to 
4096 when $NT \in \{4, 8\}$ and to 
6144 when $NT \in \{16, 32, 64\}$. 
These sizes are large enough to make GEMM run stably at peak performance
the given the total number of threads participating in the computation.
